{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-09-10 documents/supplemental.tex
finally

A small vial of liquid has a much larger surface area relative to its thermal mass. sis removed, the temperature drops very rapidly; if the temperature drops outside the physiological range of about 33-40 C, growth is stunted.\cite{effect2003}

@@

@@

The 8-bit resolution of most cameras did not seem sufficient to discern the turbidity.

\cite{Vision2016} use an ingenious technique.

>>>>

A small vial of liquid has a much larger surface area relative to its thermal mass. sis removed, the temperature drops very rapidly; if the temperature drops outside the physiological range of about 33-40 C, growth is stunted \cite{effect2003}. \cite{growth1946}.

@@

Even slight rotation of the tube, such that the graduations

"Chromogenic" substances \cite{Fluorogenic1991}, or the degradation of various dyes like Methylene Blue.

@@

The 8-bit resolution and dynamic range of most cameras did not seem sufficient to discern the turbidity; and masking and correcting for

\cite{Vision2016} use an ingenious technique. A background with sharp light-to-dark edges is used. Slicing the image into chunks only slightly larger than the object,

Another very interesting technique is that of \cite{Study2003},
